BarnebyLives an R package to create herbarium specimen labels

### 2023-09-04 manuscript/manuscript_APPS.rmd
modded  column headers in text file for simple example

```{r load libraries}
library(tidyverse) # data operations
library(sf) # spatial data
library(BarnebyLives) # for helping accession collections
```

@@

test_data <- read.csv('data/test_data.csv', na.strings = "") %>% 
  drop_na(longitude) %>% 
  drop_na(latitude) %>% 
  drop_na(date_digital) %>% 
  st_as_sf(coords = c('longitude', 'latitude'), crs = 4326)

n_families <- test_data %>% 
  st_drop_geometry() %>% 
  group_by(family) %>% 
  count() %>% 
  nrow() # 74 families

n_spp <- test_data %>% 
  st_drop_geometry() %>% 
  group_by(binomial) %>% 
  count() %>% 
  nrow() # 616 species

n_infraspecies <- test_data %>% 
  st_drop_geometry() %>% 
  drop_na(infraspecies) %>% 
  group_by(binomial, infraspecies) %>% 
  count() %>% 
  nrow() # 66 distinct infraspecies

n_sp_authors <- test_data %>% 
  st_drop_geometry() %>% 
  drop_na(authority) %>% 
  count() # 557 groups of authors

n_infra_sp_auths <- test_data %>% 
  st_drop_geometry() %>% 
  drop_na(authority1) %>% 
  group_by(binomial, infraspecies) %>% 
  count() %>% 
  nrow() # 22 distinct infra species author groups
```
```{r Run pipeline with all steps and benchmarking, eval = F}

system.time({ # if neccessary convert coordinates in degrees minutes second to decimal degrees
  data <- dms2dd(data, dms = F)
})

@@

time_political_grabber <- system.time({ # grab political information for collection
  political_grabber(data, y = 'Collection_number', path = p)
})

time_physical_grabber <- system.time({ # grab sites physical information
  data <- physical_grabber(data, path = p)
})

time_site_writer <- system.time({ # write site location notes
  data <- site_writer(data, path = p)
})

time_directions_grabber <- system.time({ # write directions to sites
  SoS_gkey = Sys.getenv("Sos_gkey")
  data <- directions_grabber(data, api_key = SoS_gkey)
})

time_spell_check <- system.time({ # ensure appropriate spellings at taxonomic levels
  data <- spell_check(data, path = p)
})

time_author_check <- system.time({ # ensure authorities are spelled-noted correctly
  data <- author_check(data, path = p)
})

time_powo_searcher <- system.time({ # search for synonyms from plants of the world online

names <- sf::st_drop_geometry(data) %>% 
  pull(Full_name)

pow_res <- lapply(names,
      powo_searcher) %>% 
  bind_rows()
data <- bind_cols(data, pow_res)

rm(names, pow_res)
})

>>>>

```{r load libraries}
library(tidyverse) # data operations
# devtools::install_github('sagesteppe/BarnebyLives')
library(BarnebyLives) # for helping accession collections
```

@@

data <- read.csv('data/test_data.csv', na.strings = "") %>% 
  drop_na(c('longitude', 'latitude', 'date_digital'))

n_families <- data %>% 
  group_by(family) %>% 
  count() %>% 
  nrow() # 74 families

n_spp <- data %>% 
  group_by(binomial) %>% 
  count() %>% 
  nrow() # 616 species

n_infraspecies <- data %>% 
  drop_na(infraspecies) %>% 
  group_by(binomial, infraspecies) %>% 
  count() %>% 
  nrow() # 66 distinct infraspecies

n_sp_authors <- data %>% 
  drop_na(authority) %>% 
  count() # 557 groups of authors

n_infra_sp_auths <- data %>% 
  drop_na(authority1) %>% 
  group_by(binomial, infraspecies) %>% 
  count() %>% 
  nrow() # 22 distinct infra species author groups

```{r Run pipeline with all steps and benchmarking, eval = F}

time_dms2dd <- system.time({ # if necessary convert coordinates in degrees minutes second to decimal degrees
  data <- dms2dd(data, dms = F)
})

time_autofill_checker <- system.time({ # has the spreadsheet software auto-incremented coordinate values?
  data <- autofill_checker(data)
})

@@

p2geo <- '/media/steppe/hdd/Barneby_Lives-dev/geodata'

time_political_grabber <- system.time({ # grab political information for collection
  data <- political_grabber(data, y = 'Collection_number', path = p2geo)
})

time_physical_grabber <- system.time({ # grab sites physical information
  data <- physical_grabber(data, path = p2geo)
}) # not finding slope and aspect

time_site_writer <- system.time({ # write site location notes
  data <- site_writer(data, path = p2geo)
})

# time_directions_grabber <- system.time({ # write directions to sites
#   SoS_gkey = Sys.getenv("Sos_gkey")
#   data <- directions_grabber(data, api_key = SoS_gkey)
# })

p2tax <- '/media/steppe/hdd/Barneby_Lives-dev/taxonomic_data'

time_spell_check <- system.time({ # ensure appropriate spellings at taxonomic levels
  data <- spell_check(data, path = p2tax)
})

time_author_check <- system.time({ # ensure authorities are spelled-noted correctly
  data <- author_check(data, path = p2tax)
})

# time_powo_searcher <- system.time({ # search for synonyms from plants of the world online

# names <- sf::st_drop_geometry(data) %>% 
#   pull(Full_name)

# pow_res <- lapply(names,
#       powo_searcher) %>% 
 #  bind_rows()
# data <- bind_cols(data, pow_res)

# rm(names, pow_res)
# })
